Relationships in the extremes and their influence on competition and coexistence

### 2021-09-30 paper/Paper.Rnw
finished revisions

%G2 
Fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms), Fig.
\ref{fig:fig3} shows that the ATA term of (\ref{eq:full_decomp}) often, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[E \nat C]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels A-D), for which the two species were equal 
competitors, storage effects (blue plus red
lines on Fig. \ref{fig:fig3}) were the only means by which coexisitence could occur, and ATA effects
tended to be negative, weakening total storage effects.

%G3
Fulfilling goal G3 of the Introduction (to explore, using the lottery model, whether species
can coexist with ATAs, but not without, or vice versa), our results show that ATAs can, indeed, sometimes
make the difference between coexistence and exclusion; both ``ATA rescue'' and ``ATA
exclusion'' (see Methods) are possible.
For some of the panels on Fig. \ref{fig:fig3}, the IGR line falls between the ATA
line and the $x$ axis for some values of $\sigma$, e.g., see panel H. 
Such cases correspond to parameter combinations
for which the presence or absence of ATAs determine whether the species coexist or not. In the 
case of panel H, for values of $\sigma$ around $4$, 
species 1 is excluded with ATAs but the two species can coexist without ATAs. 
Fig. \ref{fig:fig4} highlights additional examples. Orange lines on Fig. \ref{fig:fig4}
represent the IGR when the effects of ATAs are included, and blue lines are the IGR when
the effects of ATAs are removed. These two lines frequently crossed the $x$ axis in 
different places, showing that both ATA rescue space and ATA exclusion space can be non-empty
subsets of our trait-difference space (see Methods). For the parameters we considered, 
both ATA rescue and exclusion were more common for larger values of $\sigma$.
ATA rescue appeared more likely for smaller $\delta$, whereas ATA exclusion appeared
more common for larger $\delta$. Although bands of ATA rescue or exlusion on Fig.
\ref{fig:fig4} appear narrow, they nevertheless do occur, which means ATAs can mean the 
difference between coexistence and extirpation of one species in some cases.

@@

>>>>

%G2 
Fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms), Fig.
\ref{fig:fig3} shows that the ATA term of (\ref{eq:full_decomp}) often, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[E \nat C]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels A-D), for which the two species were equal 
competitors, storage effects (blue plus red
lines on Fig. \ref{fig:fig3}) were the only means by which coexistence could occur, and ATA effects
tended to be negative, weakening total storage effects.

%G3
Fulfilling goal G3 of the Introduction (to explore, using the lottery model, whether species
can coexist with ATAs, but not without, or vice versa), our results show that ATA can, indeed, sometimes
make the difference between coexistence and exclusion; both ``ATA rescue'' and ``ATA
exclusion'' (see Methods) are possible.
For some of the panels on Fig. \ref{fig:fig3}, the IGR line falls between the ATA
line and the $x$ axis for some values of $\sigma$, e.g., see panel H. 
Such cases correspond to parameter combinations
for which the presence or absence of ATAs determine whether the species coexist or not. In the 
case of panel H, for values of $\sigma$ around $4$, 
species 1 is excluded with ATAs but the two species can coexist without ATAs. 
Fig. \ref{fig:fig4} highlights additional examples. Orange lines on Fig. \ref{fig:fig4}
represent the IGR when the effects of ATAs are included, and blue lines are the IGR when
the effects of ATAs are removed. These two lines frequently crossed the $x$ axis in 
different places, showing that both ATA rescue space and ATA exclusion space can be non-empty
subsets of our trait-difference space (see Methods). For the parameters we considered, 
both ATA rescue and exclusion were more common for larger values of $\sigma$.
ATA rescue appeared more likely for smaller $\delta$, whereas ATA exclusion appeared
more common for larger $\delta$. Although bands of ATA rescue or exclusion on Fig.
\ref{fig:fig4} appear narrow, they nevertheless do occur, which means ATAs can mean the 
difference between coexistence and extirpation of one species in some cases.

@@

%Higher sigma means a more fluctuating and variable environment. Then, if environmental fluctuations become more variable, the effect of ATAs becomes more important and non-negligible (rescue or exclusion). 
%Delta=1 means no overlapping generations -  breaking the storage effect requirement of buffered population growth.

%Knowledge of stochastic structure (Shoemaker et al 2020)
